Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Edited Juri's section
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1643 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\noindent
Unlike GHKM, SAMT has the same coverage as Hiero, because it allows non-constituent phrases to get syntactic
labels using CCG-style slash notation. 
The derivations created using syntactically motivated grammars exhibit more coherent syntactic structure than Hiero and typically result in better reordering, especially for languages with word orders that diverge from English, like Urdu.

>>>>

\noindent
Unlike GHKM \cite{Galley2004}, SAMT has the same coverage as Hiero, because it allows non-constituent phrases to get syntactic
labels using CCG-style slash notation. Experimentally, we have found that the derivations created using syntactically motivated grammars exhibit more coherent syntactic structure than Hiero and typically result in better reordering, especially for languages with word orders that diverge from English, like Urdu \cite{SCALE-report}.
